Fourmile Calibrations and Output

### 2025-01-30 fourmile_output_dec2024.Rmd
1:1 and residual plots for statn_all & grid_all, updated KGE and pbias all model plots

@@

@@

ggplot(flow_plot_updated, aes(x = model_run, y = year, fill = kge)) +
  geom_tile(color = "white") +
  scale_fill_viridis_c(option = "viridis", name = "KGE", direction = -1) +
  geom_text(aes(label = round(kge, 2)), color = "grey", size = 2.5) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(y = "Year")

@@

ggplot(flow_plot_updated, aes(x = model_run, y = year, fill = pbias)) +
  geom_tile(color = "white") +
   scale_fill_gradient2(low = "blue", mid = "white", high = "red", midpoint = 0, name = "Pbias") +
  geom_text(aes(label = round(pbias, 2)), color = "black", size = 2.5) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(y = "Year")

@@

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=catchmentRD1_w), size =1) +
  facet_wrap(~year, scales = 'free', ncol = 2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('RD1') +
  theme(text = element_text(size = 20)) +
  labs(y = 'RD1 (mm)')

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=catchmentRD2_w), size =1) +
  facet_wrap(~year, scales = 'free', ncol = 2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('RD2') +
  theme(text = element_text(size = 20))+
  labs(y = 'RD2 (mm)')

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=catchmentRG1_w), size =1) +
  facet_wrap(~year, scales = 'free', ncol = 2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('RG1') +
  theme(text = element_text(size = 20)) +
  labs(y = 'RG1 (mm)')

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=catchmentRG2_w), size =1) +
  facet_wrap(~year, scales = 'free', ncol=2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('RG2') +
  theme(text = element_text(size = 20))+
  labs(y = 'RG2 (mm)')

@@

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=RD1cumsum), size =1) +
  facet_wrap(~year, scales = 'free', ncol=2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('Cumulative RD1 (mm)') +
  theme(text = element_text(size = 20))

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=RD2cumsum), size = 1) +
  facet_wrap(~year, scales = 'free', ncol=2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('Cumulative RD2 (mm)') +
  theme(text = element_text(size = 20))

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=RG1cumsum), size  = 1) +
  facet_wrap(~year, scales = 'free', ncol = 2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('Cumulative RG1 (mm)') +
  theme(text = element_text(size = 20))

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=RG2cumsum), size =1) +
  facet_wrap(~year, scales = 'free', ncol = 2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('Cumulative RG2 (mm)') +
  theme(text = element_text(size = 20))

@@

ggplot(gw, aes(x=date)) +
  geom_line(aes(y=RG2cumsum, color = 'cumulative RG2'), size =1) +
  geom_line(aes(y=RG1cumsum, color = 'cumulative RG1'), size =1) +
  geom_line(aes(y=RD1cumsum, color = 'cumulative RD1'), size =1) +
  geom_line(aes(y=RD2cumsum, color = 'cumulative RD2'), size =1) +
  scale_x_date(labels = date_format("%b")) +
  facet_wrap(~year + source, scales = 'free_x', ncol=2) +
  ggtitle('Cumulative RD and RG (mm)') +
  theme(text = element_text(size = 24))

@@

ggplot(gw_maxcumsum, aes(x = flow_type, y = flow_cms, fill = source)) +
  geom_boxplot(position = position_dodge(1)) +
  geom_point(position=position_jitterdodge(),alpha=0.3) +
  ggtitle('Annual sum') +
  labs(y = 'mm of water')

ggplot(gw_maxcumsum, aes(x = flow_type, y = flow_cms, fill = source)) +
  geom_boxplot(position = position_dodge(1)) +
  geom_point(position=position_jitterdodge(),alpha=0.3) +
  #geom_point(aes(color = source)) +
  facet_wrap(~flow_type, scales = 'free') +
  ggtitle('Annual sum') +
  labs(y = 'mm of water')

>>>>

write_csv(params, '/Users/megansears/Documents/Repos/fourmile/38HRU_dec2024_updates/params_unburn.csv')

@@

Q 1:1  and residual plots

```{r}

flowComp <- flow %>%
  dplyr::select(date,obs, statn_all, grid_all) %>%
  drop_na(obs) %>% 
  mutate(month = month(date)) %>%
  mutate(statn_res = obs - statn_all,
         grid_res = obs - grid_all)

statn_comp <- ggplot(flowComp) +
  geom_point(aes(x=obs, y = statn_all, color=as.factor(month))) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "red")

ggplotly(statn_comp)

grid_comp <- ggplot(flowComp) +
  geom_point(aes(x=obs, y = grid_all, color = as.factor(month))) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "red") +
  ylim(0,5)

ggplotly(grid_comp)

statn_res <- ggplot(flowComp) + geom_point(aes(x=obs, y = statn_res, color = as.factor(month))) +
  theme_bw(base_size = 20) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "red")

ggplotly(statn_res)

ggplot(flowComp) + geom_point(aes(x=obs, y = grid_res, color = as.factor(month))) +
  theme_bw(base_size = 20)+
    geom_hline(yintercept = 0, linetype = "dashed", color = "red")

grid_res <- ggplot(flowComp) + geom_point(aes(x=obs, y = grid_res, color = as.factor(month))) +
  theme_bw(base_size = 20) + ylim(-5,6)+
    geom_hline(yintercept = 0, linetype = "dashed", color = "red")

ggplotly(grid_res)

@@

flow_plot_updated <- flow_plot_updated %>%
  mutate(kge_revise = if_else(kge < 0, 0, kge))

ggplot(flow_plot_updated, aes(x = model_run, y = year, fill = kge_revise)) +
  geom_tile(color = "white") +
  scale_fill_viridis_c(option = "mako", name = "KGE", direction = -1) +
  geom_text(aes(label = round(kge_revise, 2)), color = "grey", size = 2.5) +
  theme_bw(base_size=20) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(y = "Year")

@@

ggplot(flow_plot_updated, aes(x = model_run, y = year, fill = pbias)) +
  geom_tile(color = "white") +
   scale_fill_gradient2(low = "blue", mid = "white", high = "red", midpoint = 0, name = "Pbias") +
  geom_text(aes(label = round(pbias, 2)), color = "black", size = 2.5) +
  theme_bw(base_size=20) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(y = "Year")

@@

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=catchmentRD1_w), size =1) +
  facet_wrap(~year, scales="free", ncol = 2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('RD1') +
  theme(text = element_text(size = 20)) +
  labs(y = 'RD1 (mm)') +
  theme_bw(base_size=20)

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=catchmentRD2_w), size =1) +
  facet_wrap(~year, scales = 'free', ncol = 2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('RD2') +
  theme(text = element_text(size = 20))+
  labs(y = 'RD2 (mm)')+
  theme_bw(base_size=20)

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=catchmentRG1_w), size =1) +
  facet_wrap(~year, scales = 'free', ncol = 2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('RG1') +
  theme(text = element_text(size = 20)) +
  labs(y = 'RG1 (mm)')+
  theme_bw(base_size=20)

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=catchmentRG2_w), size =1) +
  facet_wrap(~year, scales = 'free', ncol=2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('RG2') +
  theme(text = element_text(size = 20))+
  labs(y = 'RG2 (mm)')+
  theme_bw(base_size=20)

@@

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=RD1cumsum), size =1) +
  facet_wrap(~year, scales = 'free', ncol=2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('Cumulative RD1 (mm)') +
  theme(text = element_text(size = 20)) +
  theme_bw(base_size=20)

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=RD2cumsum), size = 1) +
  facet_wrap(~year, scales = 'free', ncol=2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('Cumulative RD2 (mm)') +
  theme(text = element_text(size = 20))+
  theme_bw(base_size=20)

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=RG1cumsum), size  = 1) +
  facet_wrap(~year, scales = 'free', ncol = 2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('Cumulative RG1 (mm)') +
  theme(text = element_text(size = 20))+
  theme_bw(base_size=20)

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=RG2cumsum), size =1) +
  facet_wrap(~year, scales = 'free', ncol = 2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('Cumulative RG2 (mm)') +
  theme(text = element_text(size = 20))+
  theme_bw(base_size=20)

@@

gw %>%
  filter(source == 'grid_all') %>%
  ggplot(aes(x=date)) +
  geom_line(aes(y=RG2cumsum, color = 'cumulative RG2'), size =1) +
  geom_line(aes(y=RG1cumsum, color = 'cumulative RG1'), size =1) +
  geom_line(aes(y=RD1cumsum, color = 'cumulative RD1'), size =1) +
  geom_line(aes(y=RD2cumsum, color = 'cumulative RD2'), size =1) +
  scale_x_date(labels = date_format("%b")) +
  facet_wrap(~year, scales = 'free_x', ncol=3) +
  ggtitle('Grid Cumulative RD and RG (mm)') +
  #theme(text = element_text(size = 24)) +
  theme_bw(base_size=14) +
  labs(y='cumulative sum')

gw %>%
  filter(source == 'statn_all') %>%
  ggplot(aes(x=date)) +
  geom_line(aes(y=RG2cumsum, color = 'cumulative RG2'), size =1) +
  geom_line(aes(y=RG1cumsum, color = 'cumulative RG1'), size =1) +
  geom_line(aes(y=RD1cumsum, color = 'cumulative RD1'), size =1) +
  geom_line(aes(y=RD2cumsum, color = 'cumulative RD2'), size =1) +
  scale_x_date(labels = date_format("%b")) +
  facet_wrap(~year, scales = 'free_x', ncol=3) +
  ggtitle('Statn Cumulative RD and RG (mm)') +
  #theme(text = element_text(size = 24)) +
  theme_bw(base_size=14) +
  labs(y='cumulative sum')

@@

ggplot(gw_maxcumsum, aes(x = flow_type, y = flow_cms, fill = source)) +
  geom_boxplot(position = position_dodge(1)) +
  #geom_point(position=position_jitterdodge(),alpha=0.3) +
  ggtitle('Annual sum') +
  labs(y = 'mm of water') + theme_bw(base_size=20)

ggplot(gw_maxcumsum, aes(x = flow_type, y = flow_cms, fill = source)) +
  geom_boxplot(position = position_dodge(1)) +
  #geom_point(position=position_jitterdodge(),alpha=0.3) +
  #geom_point(aes(color = source)) +
  facet_wrap(~flow_type, scales = 'free') +
  ggtitle('Annual sum') +
  labs(y = 'mm of water') + theme_bw(base_size=20)
